Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
minimally describe bridges
email addresses, no clue how to fit affiliations

\authorinfo{Carl Friedrich Bolz \and Antonio Cuni \and Maciej Fijałkowski \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de XXX}

@@

Boxing of primitive types means that dynamic languages need to be able to handle
all objects, even integers, floats, bools etc. in the same way as user-defined
instances. Thus those primitive types are usually \emph{boxed}, i.e. a small
heap-structure is allocated for them, that contains the actual value. Boxing
primitive types can be very costly, because a lot of common operations,
particularly all arithmetic operations, have to produce a new box, in addition
to the actual computation they do. Because the boxes are allocated on the heap,
producing a lot of them puts pressure on the garbage collector.

@@

bridges?

arguments to traces

getting from the interpreter to traces

>>>>

\authorinfo{Carl Friedrich Bolz \and Antonio Cuni \and Maciej Fijałkowski \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de, antocuni@gmail.com, fijal@merlinux.eu,
           samuele.pedroni@gmail.com, arigo@tunes.org}

@@

Boxing of primitive types means that dynamic languages need to be able to handle
all objects, even integers, floats, booleans etc. in the same way as user-defined
instances. Thus those primitive types are usually \emph{boxed}, i.e. a small
heap-structure is allocated for them, that contains the actual value. Boxing
primitive types can be very costly, because a lot of common operations,
particularly all arithmetic operations, have to produce a new box, in addition
to the actual computation they do. Because the boxes are allocated on the heap,
producing a lot of them puts pressure on the garbage collector.

@@

If one specific guard fails often enough, the tracing JIT will generate a new
trace that starts exactly at the position of the failing guard. The existing
assembler is patched to jump to the new trace when the guard fails
\cite{andreas_gal_incremental_2006}.
